 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-05-01 paper.Rmd
update words

A tour allows us to explore the set of all $d$-dimensional subspaces via the projection of $X$ onto $A$. 
]

---

# How does it work?

.large[
We visualise the sequence of low dimensional projections:

@@

as animated scatter or density plots. 
]

---

.large[**Grand Tour:** generate a set of random orthnormal bases, interpolate between them.]

```{r basis-view, out.width="50%", echo = FALSE}
include_graphics("img/bases-generation.png")
```

(From _Buja, Cook, Asimov and Hurley, 2004_)
---

class: middle

.large[The tour is enhanced by **interactivity**:

>>>>

A tour allows us to explore the set of all $d$-dimensional subspaces via the projection of $X$ onto $A$.

We visualise the sequence of low dimensional projections:

@@

as animated scatter or density plots.

**Grand Tour:** generate a set of random orthnormal bases, interpolate between them.

The tour is enhanced by **interactivity**:
